---
title: "Question 1"
author: "Tuwilika Keendjele"
date: "31 August 2016"
output: html_document
---

```{r question1, echo=TRUE}
library(readr)
library(tidyr)
library(dplyr)
# Import data
x <- read.csv("question1.csv")
x

# Tidy data
x1 <- boxplot(x$male, x$female, data = x, names = c("males", "females"))
x1

# Statistical test
t.test(x$male, x$female, data = x, paired = FALSE)



```
## Hypotheses
* H0 : the heart rate does not increase with body temperature
* H1 : the heart rate does increase with body temperature

## Type of data
* Unpaired, continuous data

## Statistical test
* Unpaired t-test

## Test assumptions
* Comparing two, unpaired groups

## Test output
df = 116
p-value = 0.5287

## Test interpretation
* p-value>0.05, therefore accept null hypothesis, and reject alternative hypothesis

```
```{r}
```{r question2,echo=TRUE}
library(tidyr)
library(dplyr)

# Import data
q2 <- read.csv("question2.csv")
q2

# Tidy data
head(q2)
y <- xtabs(~sex + handedness + first_stumble + final_position, data = q2)
y

# Generalised linear model
z <- glm(sex~., family = binomial(link = "logit"), data = y)
z

# Statistical test




```
## Hypotheses
* H0 : Intoxication did not affect handedness and ataxic walkng
* H1 : Intoxication did affect handedness and ataxic walking 

## Type of data
* Categorical, nominal data which is binary

## Statistical test
*

## Test assumptions
*

## Test Output


## Test conclusion
```


```
```{r}
# Import data
goo <- read.csv("question3.csv")
goo

# Tidy data
plot(goo$time ~ goo$run, type ="l", col = 'purple', xlab = 'Run number', ylab = 'Running time(s)')
lines(goo$calories, col = 'black')

# Statistical test
runanov <- aov(goo$run ~ goo$time + goo$calories)
summary(runanov)

```
## Hypotheses
* H0 : There is no correlation between number of runs with running time and calories consumed
* H1 : There is a correlation between number of runs with running time and calories consumed

## Type of data
* Paired, parametric data of 3groups

## Statistical test
* Repeated-measures anova

## Test Assumptions
* data is paired and has 2 independent variables

## Test outcome
* Df= 1
* p-value > 0.05

## Test conclusion
* p-value is > 0.05, therefore accept null hypothesis and reject alternative hypothesis

```{r question4}
foo <- rnorm(10000, mean = 60, sd = 3) # final mark
bar <- rnorm(10000, mean = 68, sd = 5) # project mark
baz <- rep(seq(from = 1997, to = 2006), each = 1) # years

year <- sample(baz, 150, replace = TRUE,
               prob = c(0.05, 0.05, 0.08, 0.08, 
                          0.1, 0.13, 0.14, 0.13, 0.12, 0.12))
project_mark <- sample(bar, 150, replace = TRUE)
final_mark <- sample(foo, 150, replace = TRUE)

plot_data <- data_frame(year = year,
                        project_mark = round(project_mark, 1),
                        final_mark = round(final_mark, 1)) %>%
arrange(year)
foo1 <- lm(plot_data$project_mark ~ plot_data$year, data = plot_data)
summary(foo1)

plot(year, project_mark, xlab = "Year", ylab = "Project mark", pch = 19, main = 'Physiology course marks')
plot(year, final_mark, xlab = "Year", ylab = "Final mark", main = 'Physiology final marks')

```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
